Modelling BCG vaccination in the UK

### 2019-12-10 rmds/08-model-development.Rmd
minor corrections complete

```{r contact-tile-plot, out.width = "250px", fig.scap = "a.) Mean contacts (non-unique social contacts per year) and the b.) normalised standard deviation (\\%) of 1000 boostrapped samples of social contacts from the POLYMOD social contact survey using 5 year age groups up 49 years old and then a single group for 50-69 year olds.", fig.cap = "a.) Mean contacts (non-unique social contacts per year) and the b.) normalised standard deviation (\\%) of 1000 boostrapped samples of  social contacts from the POLYMOD social contact survey using 5 year age groups up 49 years old and then a single group for 50-69 year olds. Mixing is highly assortative by age with children and young adults representing the majority of contacts. There is also evidence of mixing between children and middle age adults with older children mixing with progressivly older adults. Contact rates in older adults are highly uncertain, with the most uncertainty in mixing between older adults and young children."}
knitr::include_graphics(file.path(resources_path, "resources", "figure", "contact_matrix.png"))
```

@@

The semi-stochastic transmission dynamic model of TB transmission and BCG vaccination presented in this chapter provides a detailed overview of the features required to reproduce the observed epidemiology of TB in England. The model was robustly parameterised using routine surveillance data where available and otherwise using literature sources. The assumptions required by the model can be explored by fitting the model to observed data and assessing the goodness of fit. This is the focus of the next chapter. In addition the model may also be used to explore the impact of current and historic BCG vaccination policy, both in the observed data and projected into the future.Both of these scenarios are explored in the final chapter of this thesis.

>>>>

```{r contact-tile-plot, out.width = "250px", fig.scap = "a.) Mean contacts (non-unique social contacts per year) and the b.) normalised standard deviation (\\%) of 1000 boostrapped samples of social contacts from the POLYMOD social contact survey using 5-year age groups up to 49 years old and then a single group for 50-69 year olds.", fig.cap = "a.) Mean contacts (non-unique social contacts per year) and the b.) normalised standard deviation (\\%) of 1000 boostrapped samples of  social contacts from the POLYMOD social contact survey using 5 year age groups up 49 years old and then a single group for 50-69 year olds. Mixing is highly assortative by age with children and young adults representing the majority of contacts. There is also evidence of mixing between children and middle age adults with older children mixing with progressivly older adults. Contact rates in older adults are highly uncertain, with the most uncertainty in mixing between older adults and young children."}
knitr::include_graphics(file.path(resources_path, "resources", "figure", "contact_matrix.png"))
```

@@

The semi-stochastic transmission dynamic model of TB transmission and BCG vaccination presented in this chapter provides a detailed overview of the features required to reproduce the observed epidemiology of TB in England. The model was robustly parameterised using routine surveillance data where available and otherwise using literature sources. The assumptions required by the model can be explored by fitting the model to observed data and assessing the goodness of fit. This is the focus of the next chapter. In addition the model may also be used to explore the impact of current and historic BCG vaccination policy, both in the observed data and projected into the future. Both of these scenarios are explored in the final chapter of this thesis.
